Data Specialization for a Staged Lambda Calculus

### 2015-02-27 paper/splitting.tex
few more lines of splitting

\newpage

@@

\paragraph{Tuple} 
For an example with more than one argument, consider a tuple $\tup{e_1,e_2}$,
where $\diaone {e_1} \xi {v_1} \vsplito \mval {i_1} {q_1}$
and $\diaone {e_2} \xi {v_2} \vsplito \mval {i_2} {q_2}$.
The splitting invariants for $e_1$ and $e_2$ give
\[
	\splitone {e_i} A {c_i} {l_i.r_i} \text{ and } \reduce {c_i} {\tup{i_i,b_i}} \text{ and } [b_i/l_i]r_i \equiv q_i
\]
for $i=1,2$.

>>>>

@@

\paragraph{Tuple} 
For an example with more than one argument, consider a tuple $\tup{e_1,e_2}$,
where $\diaone {e_k} {\xi_k} {v_k}$ and $\rtab {\xi_k} {v_k} \vsplito \mval {i_k} {q_k}$
for $k = 1,2$.
Likewise, the splitting invariants for $e_1$ and $e_2$ give
\[
	\splitone {e_k} A {c_k} {l_k.r_k} \text{ and } \reduce {c_k} {\tup{i_k,b_k}} \text{ and } [b_k/l_k]r_k \equiv q_k
\]
Since $\diaone {\tup{e_i,e_2}} {\xi_1,\xi_2} {\tup{v_1,v_2}}$ 
and $\rtab {\xi_1,\xi_2} {\tup{v_1,v_2}} \vsplito \mval {\tup{i_1,i_2}} {\tup{q_1,q_2}}$,
the validity of the split $\splitone {\tup{e_1,e_2}} A {c'} {l.r'}$ requires,
\[
	\reduce {c'} {\tup{\tup{i_1,i_2},b'}} \text{ and } [b'/l]r' \equiv q
\]
